### 2013-12-06 paper/paper.tex
revision

We tested the bug and dart stimuli in two separate sessions with different subject samples. 
%We refer to these as Experiment 1 and Experiment 2 respectively. %ms oder auch nicht...
An experiment session consisted of 3 blocks with 42 trials per block.  
Overview of all conditions and the amount of obtained data is shown in table \ref{tab:data}. For some subjects not all blocks were run. This was  because the fixed time for the experiment have been exceeded. 

@@

\subsection*{Statistical Modeling}
In the analyses reported below we follow the approach advocated in \cite{gelman07} and \cite{gelman13}. 
We first design a model that appropriately describes the data. 
We use posterior predictive checking to decide whether the model is acceptable. 
We start by fitting a separate model for each subject. 
We then design a hierarchical model that pools data across subjects \cite{lee11a}. 
Hierarchical models can be easily formulated within bayesian framework and are evaluated with sampling algorithms.
Finally we report and interpret the estimates of population variables that are of theoretical interest. Where not specifically mentioned, we report the mean estimate and the 95 \% interval.\\
The main advantage of this approach is that it gives us flexibility to design complex models that match (or at least approach) the complexity of the processes that generated the data.
The model design involves decisions which may considerably alter the posterior estimates and even the conclusions of the analysis.
We discuss some of the modeling decisions below. 
The analyses are documented and can be replicated with the IPython Notebooks available from the project repository.
In general, virtually all results held at least to some degree across all the various models we evaluated and as such the main conclusions of this report are robust.\\
The analyses were performed with Python 2.7 and STAN 2.0.1.

\section*{Results}

@@

\subsection*{Distance Bisection}
\subsubsection*{Bugs}
Figure \ref{fig:b3} A shows data from trials where the nominal origin of bugs was located at zero. 
As expected, most of the measurements and subject medians are shifted towards bottom right.
We estimated the magnitude of perceived displacement on the x and y axis separately with a hierarchical model (S3.1) for bug stimuli (D1.3.1). Subjects judge the wolf as shifted by $0.25 \; [0.11,0.39]$ degrees in direction of its nose ($\mu{\mu,x}$ S3.1). % ich konnte die variablennamen in klammern auffuhren. ware das hilfreich?
Similar, the orientation of perpendicular agent also influences where subjects put the point of mid-distance. 
The perpendicular agent is perceived as shifted by $0.09\; [-0.03,0.21]$ \footnote{This would be $-0.1$ in figure \ref{fig.b3}} (S3.1 $\mu{\mu,y}$). 
The origin displacement on y axis is smaller than on x axis. 
As can be seen in figure \ref{fig:b3} not all subjects do show this displacement and as a result the estimated value is smaller and noisier.\\

@@

\section*{Figure Legends}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=15cm]{fig/exp}
\end{center}
\caption{
{\bf Task Overview}\\
A - Leave-Me-Alone task used by \cite{gao10} in Experiment 3a. 
Display consists of four quadrants. 
Three agents move randomly within each quadrant. 
In two quadrants the agents are oriented towards the green circle (here, the two quadrants on the left) and in other two perpendicular to it. 
Subject's task is to avoid contact with agents. \\
B -Location Recall. 
After 17 seconds the motion stops and one agent vanishes (in this case, the dart located to top-right from the green circle). 
The subject is asked to select the last position where he had seen the agent with a crosshair (not shown).\\ 
C - Distance Bisection task. 
Subject is asked to move the green circle such that it stays equidistant to the two randomly moving agents. 
}
\label{fig:exp}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{fig/man}
\end{center}
\caption{
{\bf Position of Shifted Origin.}
Dots and crosses show where the origin of the dart was set in Block 2 and Block 3 for the dart stimuli. 
Negative values shift the origin towards the nose while positive values shift in the opposite direction.
This choice of negative values follows the following logic. 
If people perceive the origin to be shifted by $k$ degrees in direction of the nose, then we need to shift the position of the nominal origin by $-k$ degrees so that the position of the nominal origin agrees with that of the perceived origin. 
}
\label{fig:man}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{fig/vectors}
\end{center}
\caption{
{\bf Additivity of Different Displacement factors.}
As explained in text we expect four different factors to influence displacement, namely representational gravity (black), representational momentum (blue) Lazy Hand Gravity (green) and Agent's Orientation (red). The result of the confluence of these factors is a displacement whose position is the sum of the infividual vectors. One way to visualize vector addition is to translate and superpose the individual vectors over each other so that they form a connected path. This is shown by the opaque arrows.  
}\label{fig:vectors}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{fig/b5}
\end{center}
\caption{
{\bf Recall and Localization of Static Stimuli.}
The first row shows the data from Experiment 1 while the remaining rows show data obtained with darts. 
The first column shows recalled position while the remaining columns show positions selected while the stimulus remained visible.
Each cell shows measurements that were rotated around the agents's center such that the direction of eyes/nose is alligned with the positive direction of the horizontal axis.  
Dots show individual trials while the crosses show median for each subject.  
The color of the symbols distinguishes different subjects and is consistent across columns.
The agents are drawn to scale on the background of each cell.  
The dashed line indicates the median displacement in direction of the agent's orientation. 
The shaded area shows the inter-quartile range. 
The dotted line in d-g shows the displacement of darts' center of mass.
}
\label{fig:b5}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{fig/b3}
\end{center}
\caption{
{\bf Results of the Distance Bisection task.}
The results for bugs are shown in A and for darts in B.
Each trial took 17 seconds. We discarded first 2 seconds and computed average mouse displacement with respect to the true mid-point. We 
rotate subjects' judgments around the nominal mid-point such that the wolf is located at 180 degrees and perpendicular agent is at 0 degrees. Each trial is shown above as a dot. Each cross shows an subject average. Furthermore the data from subjects are color-coded.
}
\label{fig:b3}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{fig/b3reg}
\end{center}
\caption{
{\bf Relation between the Perceived and Manipulated Displacement in the Distance Bisection Task.} The displacement on x axis is shown in A, while the displacement on y axis is shown in B. In each cell the perceived displacement (vertical axis) is shown in relation to the manipulated origin shift on the horizontal axis.  
Blue errorbars show the estimates for individual conditions. In red are shown the results of fitting a regression line to the data. The red line shows the mean estimate while the light and dark red band show respectively the 95 \% and 50 \% interval around the mean. }
\label{fig:b3reg}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{fig/vectors}
\end{center}
\caption{
{\bf Displacement in the Location Recall Task.}
Each of the four factors is shown in a separate cell. Dots show individual trials while the crosses show subject averages. Each subject is shown in different color. The measurements are rotated such that the orientation of the displacement factor across trials is alligned with the positive direction of the horizontal axis. Note, there are measurements beyond -2 and 2 degrees that are not shown.
}\label{fig:vec}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{fig/b2reg}
\end{center}
\caption{
{\bf Relation between Perceived and the Manipulated Displacement in the Location Recall task.}
This figure uses the same layout as figure \ref{fig:b3reg}. Refer to the caption of figure \ref{fig:b3reg} for details.
}\label{fig:b2reg}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{fig/lmaReg}
\end{center}
\caption{
{\bf Relation between Wolfpack avoidance and the Manipulated Displacement.}
This figure uses the same layout as figure \ref{fig:b3reg}. Refer to the caption of figure \ref{fig:b3reg} for details.
}\label{fig:lmaReg}
\end{figure}

@@

\begin{table}[!ht]
\caption{
\bf{Overview of fitted models}}
\begin{tabular}{|p{6.5cm}|p{6cm}|c|}
\hline
\centering{Observed Variables} & \centering{Model Specification} & Label\\
\hline
\centering{$\mathbf h_{t,i}$ gives the vector of displacement in the location judgment task for subject $i$ on trial $t$; $\phi_{i,t,k}$ angle giving the direction of factor $k$ on trial $t$ for subject $i$}
& \centering{$ h_{t,i}^x \sim  \mathcal{N}(\sum_k \alpha_{k,i}\cos \phi_{i,t,k}, \sigma_{h,i})$ $ h_{t,i}^y \sim  \mathcal{N}(\sum_k \alpha_{k,i} \sin \phi_{i,t,k}, \sigma_{h,i} )$ $\alpha_{k,i} \sim \mathcal{N}(\mu_{\alpha,k},\sigma_{\alpha,k}) $}& S1.1 \\
\hline
\centering{$\mathbf h_{t,i},\phi_{i,t,k}$ same as in S1.1; $d_{t,i}$ magnitude of origin shift as explained in figure \ref{fig:man}}
& \centering{$\alpha_{4,i,t} =\gamma_{i}+\beta_{i}d_{t,i} $  $\gamma_{i} ~ \sim \mathcal{N}(\mu_{\alpha,4},\sigma_{\alpha,4}) $ $\beta_{i} ~ \sim \mathcal{N}(\mu_{\beta},\sigma_{\beta})$; otherwise same as in S1.1} & S1.2\\
\hline
\centering{$w_{t,i}$ proportion of time spent in wolfpack areas by subject $i$ on trial $t$} &
\centering{$w_{t,i} \sim \mathcal{B}(\mu_i,\nu_i)$ $\mu_i \sim \mathcal{B}(\mu_{\mu},\nu_{\mu})$}& S2.1 \\
\hline
\centering{$w_{t,i}$ as in S2.1; $d_{t,i}$ as in S1.2} &
\centering{$ w_{t,i} \sim \mathcal{B}(\mu_i+\beta_i d_{t,i},\nu_i)$ $\mu_i \sim \mathcal{N}(\mu_{\mu},\sigma_\mu)$ $\beta_i \sim \mathcal{N}(\mu_{\beta},\sigma_\beta)$} & S2.2\\
\hline
\centering{$x_{t,i}, y_{t,i}$ displacement on the x and y axis of figure \ref{fig:b3} for subject $i$ on trial $t$} 
& \centering{$x_{t,i} \sim \mathcal{N}(\mu_{x,i},\sigma_{x,i})$  $y_{t,i} \sim \mathcal{N}(\mu_{y,i},\sigma_{y,i})$ $\mu_{x,i} \sim \mathcal{N}(\mu_{\mu,x},\sigma_{\mu,x})$ $\mu_{y,i} \sim \mathcal{N}(\mu_{\mu,y},\sigma_{\mu,y})$}&  S3.1\\
\hline
\centering{$x_{t,i}, y_{t,i}$ as in S3.1, $d_{t,i}$ magnitude of origin shift as explained in figure \ref{fig:man}}
& \centering{$x_{t,i} \sim \mathcal{N}(\mu_{x,i}+\beta_{x,i}d_{t,i},\sigma_{x,i})$ $y_{t,i} \sim \mathcal{N}(\mu_{y,i}+\beta_{y,i}d_{t,i},\sigma_{x,i})$  $\beta_{x,i} \sim \mathcal{N}(\mu_{\beta,x},\sigma_{\beta,x})$ $\beta_{y,i} \sim \mathcal{N}(\mu_{\beta,y},\sigma_{\beta,y})$ $\mu_{x,i},\mu_{y,i}$ as in S3.1} & S3.2\\
\hline
\end{tabular}
\begin{flushleft}
In general, greek letters are used for parameters and roman letters are used for observed variables.\\
$\mathcal{N}(\mu,\sigma)$ - gaussian distribution parametrized by mean $\mu$ and standard deviation $\sigma$\\
$\mathcal{B}(\mu,\nu)$ - beta distribution parametrized by mean proportion $\mu$ and sample size $\nu$
\end{flushleft}
\label{tab:models}
\end{table}

@@

>>>>

We tested the bug and dart stimuli in two separate sessions with different samples of subjects. 
Each experiment session consisted of 3 blocks with 42 trials per block.  
Overview of all conditions and the amount of obtained data is shown in table \ref{tab:data}. For some subjects not all blocks were run. This was  because the fixed time for the experiment had been exceeded. 

@@

\subsection*{Statistical Modeling}
In the analyses reported below we follow the approach advocated in \cite{gelman07} and \cite{gelman13}. 
We first design a model that appropriately describes the data. 
We use posterior predictive checking to decide whether the model is acceptable. 
We start by fitting simple model usally a model with separate parameters for each subject. 
We then design a hierarchical model that pools data across subjects \cite{lee11a}. 
Hierarchical models are most easily formulated and evaluated within bayesian framework.
Finally we report and interpret the estimates of variables of interest - usually the population-level estimates. 
We report the mean estimate and the 95 \% interval.\\
The main advantage of this approach is that it gives us flexibility to design complex models that match (or at least approach) the complexity of the processes that generated the data.
The model design involves decisions which may considerably alter the posterior estimates and even the conclusions of the analysis.
We discuss some of these modeling decisions in the Results section below. In general, virtually all results held at least to some degree across all the various models we evaluated and as such the main conclusions of this report are robust.\\
An overview of the models from which we report estimates is given in table \ref{tab:models}. 
Bayesian model requires formulation of prior distributions for the analysis. 
These are not included the table. 
We selected priors such that they do not influence the results of estimation. 
Usually we chose uniform priors, constrained to reasonable range of parameter values (e.g. range $[0,1]$ for mean proportion $\mu_{\mu}$ in S2.2). 
The models were evaluated with STAN 2.0.1 which fits statistical models with Markov chain Monte Carlo sampling. 
In each analysis, four chains were run and the convergence was checked by computing for each parameter an estimate of the potential scale reduction $\hat{R}$ (see \cite{gelman03} p.297). 
In all analyses and for all parameters we ensured that $\hat{R} \leq 1.2$ where $\hat{R} = 1$ upon convergence.
The analyses are documented and can be replicated with the IPython Notebooks available from the project repository.
The table \ref{tab:ip} links the reported analyses to the output in these files. 
\section*{Results}

@@

\subsection*{Distance Bisection}
\subsubsection*{Bugs}
Figure \ref{fig:b3} A shows data from trials where the nominal origin of bugs was located at zero. 
As expected, most of the measurements and subject medians are shifted towards bottom right.
We estimated the magnitude of perceived displacement on the x and y axis separately with a hierarchical model (S3.1) for bug stimuli (D1.3.1). Subjects judge the wolf as shifted by $0.25 \; [0.11,0.39]$ degrees in direction of its nose ($\mu{\mu,x}$ S3.1). % ich konnte die variablennamen in klammern auffuhren. ware das hilfreich?
Similar, the orientation of perpendicular agent also influences where subjects put the point of mid-distance. 
The perpendicular agent is perceived as shifted by $0.09\; [-0.03,0.21]$ \footnote{This would be $-0.1$ in figure \ref{fig:b3}} (S3.1 $\mu{\mu,y}$). 
The origin displacement on y axis is smaller than on x axis. 
As can be seen in figure \ref{fig:b3} not all subjects do show this displacement and as a result the estimated value is smaller and noisier.\\

@@

\section*{Figure Legends}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6.83in]{fig/exp}
\end{center}
\caption{
{\bf Task Overview}\\
A - Leave-Me-Alone task used by \cite{gao10} in Experiment 3a. 
Display consists of four quadrants. 
Three agents move randomly within each quadrant. 
In two quadrants the agents are oriented towards the green circle (here, the two quadrants on the left) and in other two perpendicular to it. 
Subject's task is to avoid contact with agents. \\
B -Location Recall. 
After 17 seconds the motion stops and one agent vanishes (in this case, the dart located to top-right from the green circle). 
The subject is asked to select the last position where he had seen the agent with a crosshair (not shown).\\ 
C - Distance Bisection task. 
Subject is asked to move the green circle such that it stays equidistant to the two randomly moving agents. 
}
\label{fig:exp}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/man}
\end{center}
\caption{
{\bf Position of Shifted Origin.}
Dots and crosses show where the origin of the dart was set in Block 2 and Block 3 for the dart stimuli. 
Negative values shift the origin towards the nose while positive values shift in the opposite direction.
This choice of negative values follows the following logic. 
If people perceive the origin to be shifted by $k$ degrees in direction of the nose, then we need to shift the position of the nominal origin by $-k$ degrees so that the position of the nominal origin agrees with that of the perceived origin. 
}
\label{fig:man}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/gao}
\end{center}
\caption{
{\bf Failed Replication.}
Dots show the average proportion of time spent in the wolfpack quadrants by subjects in our sample. 
Red line shows the mean estimate reported in \cite{gao10} and the red surface shows the 95\% interval.
}
\label{fig:gao}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/vectors}
\end{center}
\caption{
{\bf Additivity of Different Displacement factors.}
Four different factors influence the displacement (cross), namely representational gravity (black), representational momentum (blue) Lazy Hand Gravity (green) and Agent's Orientation (red). The result of the confluence of these factors is a displacement that is sum of the infividual vectors. One way to visualize vector addition is to translate and superpose the individual vectors over each other so that they form a connected path. This is shown by the opaque arrows.  
}\label{fig:vec}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6.83in]{fig/b5}
\end{center}
\caption{
{\bf Recall and Localization of Static Stimuli.}
The first row shows the data from Experiment 1 while the remaining rows show data obtained with darts. 
The first column shows recalled position while the remaining columns show positions selected while the stimulus remained visible.
Each cell shows measurements that were rotated around the agents's center such that the direction of eyes/nose is alligned with the positive direction of the horizontal axis.  
Dots show individual trials while the crosses show median for each subject.  
The color of the symbols distinguishes different subjects and is consistent across columns.
The agents are drawn to scale on the background of each cell.  
The dashed line indicates the median displacement in direction of the agent's orientation. 
The shaded area shows the inter-quartile range. 
The dotted line in D-G shows the displacement of darts' center of mass.
}
\label{fig:b5}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/b3}
\end{center}
\caption{
{\bf Results of the Distance Bisection task.}
The results for bugs are shown in A and for darts in B.
Each trial took 17 seconds. We discarded first 2 seconds and computed average mouse displacement with respect to the true mid-point. We 
rotate subjects' judgments around the nominal mid-point such that the wolf is located at 180 degrees and perpendicular agent is at 0 degrees. Each trial is shown above as a dot. Each cross shows an subject average. Furthermore the data from subjects are color-coded.
}
\label{fig:b3}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=4.86in]{fig/b3reg}
\end{center}
\caption{
{\bf Relation between the Perceived and Manipulated Displacement in the Distance Bisection Task.} The displacement on x axis is shown in A, while the displacement on y axis is shown in B. In each cell the perceived displacement (vertical axis) is shown in relation to the manipulated origin shift on the horizontal axis.  
Blue errorbars show the estimates for individual conditions. In red are shown the results of fitting a regression line to the data. The red line shows the mean estimate while the light and dark red band show respectively the 95 \% and 50 \% interval around the mean. }
\label{fig:b3reg}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=4.86in]{fig/b1}
\end{center}
\caption{
{\bf Displacement in the Location Recall Task.}
Each of the four factors is shown in a separate cell. Dots show individual trials while the crosses show subject averages. Each subject is shown in different color. The measurements are rotated such that the orientation of the displacement factor across trials is alligned with the positive direction of the horizontal axis. Note, there are measurements beyond -2 and 2 degrees that are not shown.
}\label{fig:b1}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/b2reg}
\end{center}
\caption{
{\bf Relation between Perceived and the Manipulated Displacement in the Location Recall task.}
This figure uses the same layout as figure \ref{fig:b3reg}. Refer to the caption of figure \ref{fig:b3reg} for details.
}\label{fig:b2reg}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/lmaReg}
\end{center}
\caption{
{\bf Relation between Wolfpack avoidance and the Manipulated Displacement.}
This figure uses the same layout as figure \ref{fig:b3reg}. Refer to the caption of figure \ref{fig:b3reg} for details.
}\label{fig:lmaReg}
\end{figure}

@@

\begin{table}[!ht]
\caption{
\bf{Overview of fitted models}}
\begin{tabular}{|p{6.5cm}|p{5cm}|c|}
\hline
\centering{Observed Variables} & \centering{Model Specification} & Label\\
\hline
\centering{$\mathbf h_{t,i}$ gives the vector of displacement in the location judgment task for subject $i$ on trial $t$; $\phi_{i,t,k}$ angle giving the direction of factor $k$ on trial $t$ for subject $i$}
& \centering{$ h_{t,i}^x \sim  \mathcal{N}(\sum_k \alpha_{k,i}\cos \phi_{i,t,k}, \sigma_{h,i})$ $ h_{t,i}^y \sim  \mathcal{N}(\sum_k \alpha_{k,i} \sin \phi_{i,t,k}, \sigma_{h,i} )$ $\alpha_{k,i} \sim \mathcal{N}(\mu_{\alpha,k},\sigma_{\alpha,k}) $}& S1.1 \\
\hline
\centering{$\mathbf h_{t,i},\phi_{i,t,k}$ same as in S1.1; $d_{t,i}$ magnitude of origin shift as explained in figure \ref{fig:man}}
& \centering{$\alpha_{4,i,t} =\gamma_{i}+\beta_{i}d_{t,i} $  $\gamma_{i} ~ \sim \mathcal{N}(\mu_{\alpha,4},\sigma_{\alpha,4}) $ $\beta_{i} ~ \sim \mathcal{N}(\mu_{\beta},\sigma_{\beta})$; otherwise same as in S1.1} & S1.2\\
\hline
\centering{$w_{t,i}$ proportion of time spent in wolfpack areas by subject $i$ on trial $t$} &
\centering{$w_{t,i} \sim \mathcal{B}(\mu_i,\nu_i)$ $\mu_i \sim \mathcal{B}(\mu_{\mu},\nu_{\mu})$}& S2.1 \\
\hline
\centering{$w_{t,i}$ as in S2.1; $d_{t,i}$ as in S1.2} &
\centering{$ w_{t,i} \sim \mathcal{B}(\mu_i+\beta_i d_{t,i},\nu_i)$ $\mu_i \sim \mathcal{N}(\mu_{\mu},\sigma_\mu)$ $\beta_i \sim \mathcal{N}(\mu_{\beta},\sigma_\beta)$} & S2.2\\
\hline
\centering{$x_{t,i}, y_{t,i}$ displacement on the x and y axis of figure \ref{fig:b3} for subject $i$ on trial $t$} 
& \centering{$x_{t,i} \sim \mathcal{N}(\mu_{x,i},\sigma_{x,i})$  $y_{t,i} \sim \mathcal{N}(\mu_{y,i},\sigma_{y,i})$ $\mu_{x,i} \sim \mathcal{N}(\mu_{\mu,x},\sigma_{\mu,x})$ $\mu_{y,i} \sim \mathcal{N}(\mu_{\mu,y},\sigma_{\mu,y})$}&  S3.1\\
\hline
\centering{$x_{t,i}, y_{t,i}$ as in S3.1, $d_{t,i}$ magnitude of origin shift as explained in figure \ref{fig:man}}
& \centering{$x_{t,i} \sim \mathcal{N}(\mu_{x,i}+\beta_{x,i}d_{t,i},\sigma_{x,i})$ $y_{t,i} \sim \mathcal{N}(\mu_{y,i}+\beta_{y,i}d_{t,i},\sigma_{x,i})$  $\beta_{x,i} \sim \mathcal{N}(\mu_{\beta,x},\sigma_{\beta,x})$ $\beta_{y,i} \sim \mathcal{N}(\mu_{\beta,y},\sigma_{\beta,y})$ $\mu_{x,i},\mu_{y,i}$ as in S3.1} & S3.2\\
\hline
\end{tabular}
\begin{flushleft}
In general, greek letters are used for parameters and roman letters are used for observed variables.\\
$\mathcal{N}(\mu,\sigma)$ - gaussian distribution parametrized by mean $\mu$ and standard deviation $\sigma$\\
$\mathcal{B}(\mu,\nu)$ - beta distribution parametrized by mean proportion $\mu$ and sample size $\nu$
\end{flushleft}
\label{tab:models}
\end{table}

@@

\begin{table}[!ht]
\caption{
\bf{Displacement of Static Agents}}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Analysis & Data & Model & File & Input & Output\\
\hline
A1 & D1.3.1 & S3.1 & \texttt{E1B3.ipynb} & & \\
A2 & D2.3.1 & S3.1 & \texttt{E2B3.ipynb} & & \\
A3 & \centering{D2.3.1 D2.3.2 D2.3.3} & S3.1 & \texttt{E2B3.ipynb} & & \\
A4 & \centering{D2.3.1 D2.3.2 D2.3.3} & S3.2 & \texttt{E2B3.ipynb} & & \\
\hline
\end{tabular}
\begin{flushleft}
\end{flushleft}
\label{tab:ip}
\end{table}
